 

### 2020-08-24 vertical-thermal-review.Rmd
update doc
authors
add Table 1

---
title: ''
output: word_document
bibliography: references.bib #This can be generated by exporting BibTex file from Zotero
csl: new-phytologist.csl

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

**Authors (so far):** 
Nidhi Vinod^1^
Martijn Slot^2^
Kristina J. Anderson-Teixeira^1,2^*

@@

![**Figure 4. Temperature sensitivity of tree growth for understory versus canopy trees.** Analysis methods described in Appendix S3. Data from Helcoski et al. 2019.](SCBI_tree_rings/SCBIfig.png)

>>>>

---
title: ''
output: word_document
bibliography: references.bib #This can be generated by exporting BibTex file from Zotero
csl: new-phytologist.csl 
nocite: | 
  @zellweger_seasonal_2019 
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

**Authors (so far, not necessarily in final order):** 
Nidhi Vinod^1^
Martijn Slot^2^
Ian McGregor
Elsa Ordway
Marielle Smith
Tyeen Taylor
Kristina J. Anderson-Teixeira^1,2^*

@@

![**Figure 4. Temperature sensitivity of tree growth for understory versus canopy trees.** Analysis methods described in Appendix S3. Data from Helcoski et al. 2019.](SCBI_tree_rings/SCBIfig.png)
## Implications for Modeling / Scaling
